Test SUSIE for regions near genes (500kb flanking)

### 2020-06-24 analysis/simulation-susie-ukbchr22-gtex.adipose.Rmd
susie more examples

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

  fig <- plot_ly(dt, x = ~ pos, y = ~ pip, type = 'scatter', mode = 'markers', color = ~ ifcausal, colors = pal, text = ~paste("Name: ", name))

  fig <- fig %>% layout(yaxis = list(title = "PIP"))
  return(fig)
}

plot_all <- function(susieres, mrashres.gene, mrashres.snp){
  dt <- read.table(susieres , header =T)

@@

  fig <- fig %>% layout(autosize = F, width = 600, height = 600, margin = 0.02,
    xaxis = list(title = "Genomic position"))

@@

## Simulation 1
Priors:
```{r para 1}
mrashtag <- "20200616-1"
susietag <- "20200616-1"
readLines(paste0(outputdir, "prior-", susietag, ".R"))
```

```{r sim 1 setup}
mrashres.gene <- paste0(mr.ash2dir, mrashtag, "-mr.ash2s.expr-res.expr.txt")
mrashres.snp <- paste0(mr.ash2dir, mrashtag, "-mr.ash2s.expr-res.snp.txt")
```

### SUSIE results: PIP > 0.5 or causal genes

```{r sim 1 examples, out.width = "98%", out.height="95%"}
nameall <- read.table(paste0(outputdir, "gene-flank500kb-", susietag, ".txt"))[ , 4]
for (name in nameall){
  susieres <- paste0(outputdir, susietag,"-", name, "-susieres.txt")
  print(paste0("SUISE results for regions around ", name))
  plot_all(susieres, mrashres.gene, mrashres.snp)
}
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F)
```

@@

  fig <- plot_ly(dt, x = ~ pos, y = ~ pip, type = 'scatter', mode = 'markers', color = ~ ifcausal, colors = pal, text = ~paste("Name: ", name), width = 600, height = 400)

  fig <- fig %>% layout( yaxis = list(title = "PIP"), plot_bgcolor='#ebf6fc')
  return(fig)
}

plot_all <- function(susieres, mrashres.gene, mrashres.snp, title){
  dt <- read.table(susieres , header =T)

@@

  fig <- fig %>% layout(title = title, autosize = F,  margin = 0.02,
    xaxis = list(title = "Genomic position"))

@@

## Simulation 5
```{r sim 5 setup}
tag <- "20200616-5"
tag2 <- "expr-res"
mrashres.gene <- paste0(mr.ash2dir, tag, "-mr.ash2s.", tag2, ".expr.txt")
mrashres.snp <- paste0(mr.ash2dir, tag, "-mr.ash2s.", tag2, ".snp.txt")
```

### SUSIE results: PIP > 0.3 or causal genes

```{r sim 5 examples, include= F, echo = F, eval = F, warning= F}
# displaying not right
resall <- Sys.glob(paste0(outputdir, tag, ".", tag2, "*-susieres.txt"))
l <- htmltools::tagList()
res <- resall[1]
for (i in 1:8){
  res <- resall[i]
  name <- gsub(".*res-(.+)-susie.*", "\\1", res)
  l[[i]] <- plot_all(res, mrashres.gene, mrashres.snp, name)
}
l
```

```{r sim 5 examples,  out.width = "98%", out.height="95%", warning= F}
# displaying not right
res <- paste0(outputdir, tag, ".", tag2, "-LL22NC03-86G7.1-susieres.txt")
name <- gsub(".*res-(.+)-susie.*", "\\1", res)
plot_all(res, mrashres.gene, mrashres.snp, name)
```

### 2020-06-24 analysis/simulation-susie-ukbchr22.Rmd
susie more examples

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval=T)
```

```{r plot functions}
library(mr.ash.alpha)
library(data.table)
suppressMessages({library(plotly)})

@@

  fig <- fig %>% layout(autosize = F, width = 600, height = 600, margin = 0.02,
    xaxis = list(title = "Genomic position"))

  fig <- fig %>% toWebGL()
  fig
}

```

```{r output dir}
simdatadir <- "~/causalTWAS/simulations/simulation_ashtest_20200503/"
outputdir <- "~/causalTWAS/simulations/simulation_susietest_20200604/"
mr.ash2dir <-  "~/causalTWAS/simulations/simulation_ashtest_20200527/"
```

## Simulation 1
Priors:
```{r para 1}
readLines(paste0(outputdir, "prior-1.R"))
```

SUSIE results:
```{r sim 1 setup}
mrashtag <- "20200527-1"
susietag <- "20200604-1"
mrashres.gene <- paste0(mr.ash2dir, mrashtag, "-mr.ash2s.expr-res.expr.txt")
mrashres.snp <- paste0(mr.ash2dir, mrashtag, "-mr.ash2s.expr-res.snp.txt")
```

@@

```{r sim 1 3, out.width = "98%", out.height="95%"}
name <- "DGCR14"
susieres <- paste0(outputdir, susietag,"-", name, "-susieres.txt")
print(paste0("SUISE results for regions around ", name))
plot_all(susieres, mrashres.gene, mrashres.snp)
```

```{r sim 1 4, out.width = "98%", out.height="95%"}
name <- "VPREB3"
susieres <- paste0(outputdir, susietag,"-", name, "-susieres.txt")
print(paste0("SUISE results for regions around ", name))
plot_all(susieres, mrashres.gene, mrashres.snp)
```

```{r sim 1 5, out.width = "98%", out.height="95%"}
name <- "TCN2"
susieres <- paste0(outputdir, susietag,"-", name, "-susieres.txt")
print(paste0("SUISE results for regions around ", name))
plot_all(susieres, mrashres.gene, mrashres.snp)
```

### FALSE negatives in mr.ash2
```{r sim 1 6, out.width = "98%", out.height="95%"}
name <- "CBX6"
susieres <- paste0(outputdir, susietag,"-", name, "-susieres.txt")
print(paste0("SUISE results for regions around ", name))
plot_all(susieres, mrashres.gene, mrashres.snp)
```

```{r sim 1 7, out.width = "98%", out.height="95%"}
name <- "CHEK2"
susieres <- paste0(outputdir, susietag,"-", name, "-susieres.txt")
print(paste0("SUISE results for regions around ", name))
plot_all(susieres, mrashres.gene, mrashres.snp)
```

### True positives in mr.ash2
```{r sim 1 8, out.width = "98%", out.height="95%"}
name <- "LMF2"
susieres <- paste0(outputdir, susietag,"-", name, "-susieres.txt")
print(paste0("SUISE results for regions around ", name))
plot_all(susieres, mrashres.gene, mrashres.snp)
```

```{r sim 1 9, out.width = "98%", out.height="95%"}
name <- "DDX17"
susieres <- paste0(outputdir, susietag,"-", name, "-susieres.txt")
print(paste0("SUISE results for regions around ", name))
plot_all(susieres, mrashres.gene, mrashres.snp)
```
```{r sim 1 10, out.width = "98%", out.height="95%"}
name <- "MIF"
susieres <- paste0(outputdir, susietag,"-", name, "-susieres.txt")
print(paste0("SUISE results for regions around ", name))
plot_all(susieres, mrashres.gene, mrashres.snp)
```

@@

name <- "MCM5"
susieres <- paste0(outputdir, susietag,"-", name, "-susieres.txt")
print(paste0("SUISE results for regions around ", name))
plot_all(susieres, mrashres.gene, mrashres.snp)
```

```{r sim 3 2, out.width = "98%", out.height="95%"}

name <- "CBX6"
susieres <- paste0(outputdir, susietag,"-", name, "-susieres.txt")
print(paste0("SUISE results for regions around ", name))
plot_all(susieres, mrashres.gene, mrashres.snp)
```

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(eval=T, warning = F)
```

```{r plot functions, eval=T}
library(mr.ash.alpha)
library(data.table)
suppressMessages({library(plotly)})

@@

  fig <- fig %>% layout(title = title, autosize = F,  margin = 0.02,
    xaxis = list(title = "Genomic position"))

  fig <- fig %>% toWebGL()
  fig
}
```

```{r output dir, eval=T}
simdatadir <- "~/causalTWAS/simulations/simulation_ashtest_20200503/"
outputdir <- "~/causalTWAS/simulations/simulation_susietest_20200604/"
mr.ash2dir <-  "~/causalTWAS/simulations/simulation_ashtest_20200527/"
```

## Simulation 1
```{r sim 1 setup, eval = T}
mrashtag <- "20200527-1"
susietag <- "20200604-1"
mrashres.gene <- paste0(mr.ash2dir, mrashtag, "-mr.ash2s.expr-res.expr.txt")
mrashres.snp <- paste0(mr.ash2dir, mrashtag, "-mr.ash2s.expr-res.snp.txt")
```

@@

```{r sim 1 3, out.width = "98%", out.height="95%", eval =T}
name <- "DGCR14"
susieres <- paste0(outputdir, susietag, "-", name, "-susieres.txt")
plot_all(susieres, mrashres.gene, mrashres.snp, name)
```

```{r sim 1 4, out.width = "98%", out.height="95%"}
name <- "VPREB3"
susieres <- paste0(outputdir, susietag,"-", name, "-susieres.txt")
plot_all(susieres, mrashres.gene, mrashres.snp, name)
```

```{r sim 1 5, out.width = "98%", out.height="95%"}
name <- "TCN2"
susieres <- paste0(outputdir, susietag,"-", name, "-susieres.txt")
plot_all(susieres, mrashres.gene, mrashres.snp, name)
```

### FALSE negatives in mr.ash2
```{r sim 1 6, out.width = "98%", out.height="95%"}
name <- "CBX6"
susieres <- paste0(outputdir, susietag,"-", name, "-susieres.txt")
plot_all(susieres, mrashres.gene, mrashres.snp, name)
```

```{r sim 1 7, out.width = "98%", out.height="95%"}
name <- "CHEK2"
susieres <- paste0(outputdir, susietag,"-", name, "-susieres.txt")
plot_all(susieres, mrashres.gene, mrashres.snp, name)
```

@@

name <- "MCM5"
susieres <- paste0(outputdir, susietag,"-", name, "-susieres.txt")
plot_all(susieres, mrashres.gene, mrashres.snp, name)
```

```{r sim 3 2, out.width = "98%", out.height="95%"}
name <- "CBX6"
susieres <- paste0(outputdir, susietag,"-", name, "-susieres.txt")
plot_all(susieres, mrashres.gene, mrashres.snp, name)
```

@@

## Simulation 5

```{r sim 5 setup}
tag <- "20200527-5"
tag2 <- "expr-res"
susietag <- "20200527-5"
mrashres.gene <- paste0(mr.ash2dir, tag, "-mr.ash2s.", tag2, ".expr.txt")
mrashres.snp <- paste0(mr.ash2dir, tag, "-mr.ash2s.", tag2, ".snp.txt")
```

```{r sim 5 1, out.width = "98%", out.height="95%"}
name <- "CRELD2"
susieres <- paste0(outputdir, tag, ".", tag2, "-", name, "-susieres.txt")
plot_all(susieres, mrashres.gene, mrashres.snp, name)
```
